Nowadays as more and more data is created from different heterogeneous applications there’s a need for a storage system which supports this kind of unstructured data. As Big Data is unavoidable for most global players this topic is getting more relevant today. One solution for handling unstructured data in context of Big Data is the usage of NoSQL databases. This ebook shall give a brief introduction to several NoSQL databases. Its intention is to give the reader an idea of different database types in terms of specific database examples. This ebook is supposed to be an entry point for further investigations by the reader. While it gives important information it neither provides a comparison of the presented databases nor is supposed to be a comprehensive manual. Therefore it differs the different types available.
In today’s context of NoSQL Databases we differentiate the following four types: Column-Oriented, Key-Value, Document-Oriented and Graph databases. Each of these is designed to suit the needs of different applications and their data structures. This project gives an introduction to two members of each type and it will show some use cases for them. Small expert groups of two to four students create these chapters. First the main concepts of every database are explained and sometimes special features are mentioned. Finally, advantages and disadvantages are discussed. In this project not many details are mentioned and it is only a short summary of NoSQL databases to have an overview about current technologies. Small implementation examples are provided but for further information’s it is necessary to read in bibliography.